Price of Anarchy for Mean Field Games

### 2018-08-02 PoA.tex
minor change in Theorem 2

	From equation (\ref{eq:riccati_ut_sol_deriv}) and the Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), it is easy to check that if the conditions in (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}) are satisfied, we must have $u_t = w_t$ for all $ t\in [0,T]$. Thus, $PoA = 1$.

>>>>

	From equation (\ref{eq:riccati_ut_sol_deriv}) and the uniqueness of solutions to Riccati equations (\ref{eq:riccati_ut}) and (\ref{eq:riccati_wt}), it is easy to check that if the conditions in (\ref{eq:PoA=1_condition_b1_bar>0}) and (\ref{eq:PoA=1_condition_b1_bar=0}) are satisfied, we must have $u_t = w_t$ for all $ t\in [0,T]$. Thus, $PoA = 1$.
